Lactate transport inhibition therapeutically reprograms fibroblast

### 2024-03-02 manuscript/manuscript.qmd
add aged mice histology examples

# ensure figures are up-to-date
targets::tar_load(
  c(
    fig01,
    fig02,
    fig03,
    fig04,
    fig05,
    fig06,
    fig07,
    fig08, 
    # fig10,
    # fig11,
    # resources_table,
    NULL
  )
)
```

>>>>

# ensure figures are up-to-date
targets::tar_load(
  c(
    fig01,
    fig02,
    fig03,
    fig04,
    fig05,
    fig06,
    fig07,
    fig08, 
    fig09, 
    fig10,
    # resources_table,
    NULL
  )
)
```
